Renal III

### 2017-05-25 renal3.rmd
completed short case

>>>>

Immunosuppresive agents:

-  Calcineurin inhibitors: tacrolimus and cyclosporin act and prevent IL-2 formation => no T cells
-  Antimetabolites: mycophenalate prevent B and T lymphocyte production
-  IL-2 R antag: basilixamab

Side effects: opportunistic infections, cushings, malignancy, osteoporosis (w/ glucocorticoids)

# Short case 2

42M severe right flank pain and is now all the way to his groin. Pain is coming in waves and came in 1 hour ago.

DDx: renal colic caused by kidney stones (aka nephrolithiasis), biliary colic (gall stones biliary tree), pyelonephritis, PKD => cyst rupture, (Female can be ovarian stuff), renal capsule stretched, malignancy

Colicky pain in hollow viscous with peristalsis.

Pain radiation: referred pain due to nerves such as iliohypogastric

Pathophysiology of HTN: build up of fluid => Down GFR => RAAS to increase BP. HTN is a risk factor for kidney stones

Ix to order:

-  Xray KUB: Ca stones (80-90%) are visible since it is a metal
-  Ultrasound KUB: visualise hydronephrosis (swollen proximal ureter and thin distal ureter) due to an obstruction, can see calcification, see if kidney is swollen, bladder = {stones in there?, vesicoureteral junction reflux}
-  CT KUB: if ultrasound is not diagnostic
-  CHEM20 can view the PO4, Ca2+, Mg2+, uric acid  which may cause the stone | measure eGFR which can indicate for surgery
-  Urine MCS: bacteriuria, casts/dysmorphic red cells, pyelonephritis, septic cause, maybe see crystals (oxalate)
-  FBC: white cells can indicate pyelonephritis
-  Urinalysis: proteinuria or haematuria, nitrites pathognomic of UTI (which includes pyelonephritis)

Kidney stones often made up of: Ca, oxlate, NH4+, PO4, cysteine, nitrogen compounds

Risk factors urolithiasis: Hx of gout, foods high in oxalate (beetroot, strawberries), alkaline urine (risk for uric acid stones), diabetes, immobility (stasis; such as from obstructive disease like **PKD**), males, fam Hx, drugs, dehydration

Stones can lead to infection, hydronephrosis, decreased GFR, AKI => CKD, shitload of pain, rupture of ureter

Lifestyle Mx: hydration, change diet (less of some shit, less beer), exercise

Tx:

-  Medical: lithotripsy can break the stone down if it is small enough (<2mm), alpha blockers or CCB (?!; is possible)
-  Surgery: urological surgery (by putting a stent in and allowing it to pass through

Key factor: if the stone is >10mm then operation. Not then try medical treatment
